PM Mungbean meta-analysis

### 2019-07-03 01_Meta-analysis_experiments.Rmd
clarifying information on experimental site details
update libraries
commenting out some lines

@@

## Experimental locations
```{r Experiment_locations}

>>>>

```{r MEsummary_Libraries}
library(dplyr)
library(openxlsx)
library(kableExtra)
library(ggplot2)
library(leaflet)
#source("./getPPD2.R")

@@

## Summary of data

```{r data_summary, echo=TRUE, message=FALSE, warning=FALSE}

# source("Cleaning historical data.R", echo = FALSE, print.eval = FALSE)
# ___ Datasets available ___
# data   Herm_16.DR     - mean powdery mildew Disease rating data and mean Yield from two field trials in 2017, Hermitage and Fogerty
# data   King_16.DR     - mean powdery mildew Disease rating data and mean Yield from two field trials in 2016, Hermitage and Kingaroy
# data   Fogerty_17.1   - Full disease ratings and yeild data from Fogerty field trial in 2017
# data   Herm_17.1      - Full disease ratings and yeild data from Hermitage field trial in 2017
# data   PM_MB_17       - Full disease ratings and yeild data from Hermitage and Fogerty in 2017
# data   PM_MB_16       - End of season powdery mildew rating and Yield data from two field trials in 2016, Hermitage and Kingaroy
# data   PM_MB_means    - Mean disease rating and yeild data, from trial reports

PM.dat <- read.csv("data/1902 powdery mildew-Mungbean - Collated means.csv")

glimpse(PM.dat)

kable(PM.dat %>%
   group_by(Trial_ref, Year, Location, trial_design, Replicates, planting_date, emergence_date, first_sign_disease) %>%
   summarise(Treatments = length(E_treatment)),
   caption = "Description of Experiments") %>%
   kable_styling(fixed_thead = T, full_width = T) %>%
   scroll_box(width = "900px", height = "500px")

PM.dat$Trial_ref <- factor(PM.dat$Trial_ref)
PM.dat$Location <- factor(PM.dat$Location)
PM.dat$Year <- factor(PM.dat$Year)
PM.dat$host_genotype <- factor(PM.dat$host_genotype)
PM.dat$Fungicide <- factor(PM.dat$Fungicide)
PM.dat$Trade_name <- factor(PM.dat$Trade_name)

## Experimental locations
Experimental locations where data was sufficient to include in meta-analysis
```{r Experiment_locations}
